How and Why to run a Hack Week

### 2017-09-04 paper.tex
Move Tal from authors to acknoweldgements.

\author{Daniela Huppenkothen, Anthony Arendt, David W. Hogg, Karthik Ram, Jake VanderPlas, Tal Yarkoni, \& Ariel Rokem}

@@

\begin{addendum}
 \item{The authors would like to thank Laura Nor\'{e}n (NYU) for help on ethics and IRB, Stuart Geiger for helping to formulate the questionnaires that served as the basis for the results presented here. This work was partially supported by the Moore-Sloan Data Science Environments at UC Berkeley, New York University, and the University of Washington. Neurohack week is supported through a grant from the National Institute for Mental Health (1R25MH112480). Daniela Huppenkothen is partially supported by the James Arthur Postdoctoral Fellowship at NYU.}
 \item[Competing Interests]{The authors declare that they have no competing financial interests.}
 \item[Correspondence]{Correspondence and requests for materials should be addressed to D.Huppenkothen.~(email: daniela.huppenkothen@nyu.edu).}
\end{addendum}

>>>>

\author{Daniela Huppenkothen, Anthony Arendt, David W. Hogg, Karthik Ram, Jake VanderPlas, \& Ariel Rokem}

@@

\begin{addendum}
 \item{The authors would like to thank Laura Nor\'{e}n (NYU) for help on ethics and IRB, Stuart Geiger for helping to formulate the questionnaires that served as the basis for the results presented here. Thanks to Tal Yarkoni for advice regarding automated selection procedures. This work was partially supported by the Moore-Sloan Data Science Environments at UC Berkeley, New York University, and the University of Washington. Neuro hack week is supported through a grant from the National Institute for Mental Health (1R25MH112480). Daniela Huppenkothen is partially supported by the James Arthur Postdoctoral Fellowship at NYU.}
 \item[Competing Interests]{The authors declare that they have no competing financial interests.}
 \item[Correspondence]{Correspondence and requests for materials should be addressed to D.Huppenkothen.~(email: daniela.huppenkothen@nyu.edu).}
\end{addendum}
